Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex
Totally had matthew's name mispelled :P
Typing judgements for values.  Fixed some other small bits.

\documentclass[a4paper,twocolumn]{article}

\title{Towards a Mechanized Proof of Noninterference}
\author{Tom Magrino \and Mathew Milano}
\begin{document}

@@

\abstract
Abstract goes here, summarize what this paper covers and what we ended up with.

@@

Outline the type system of the language and again compare/contrast with
Pottier and Simonet.

@@

Acknowledge people who really helped.  Primary name that comes to mind is that
nice Jon fellow we spent many hours on the phone getting advice from.

\bibliographystyle{abbrv}
\bibliography{paper.bib}

>>>>

\documentclass[a4paper,twocolumn]{article}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}

\newcommand{\langName}[0]{TinyML\textsuperscript{2}}
\newcommand{\typeRule}[3]
{#1 \textsf{ } \vdash \textsf{ } #2 \textsf{ } \colon \textsf{ } #3}

\title{Towards a Mechanized Proof of Noninterference}
\author{Tom Magrino \and Matthew Milano}
\begin{document}

@@

\abstract

Citing something for now to make an error message go away~\cite{Pierce:SF}.
Abstract goes here, summarize what this paper covers and what we ended up with.

@@

\begin{figure}
  \begin{mathpar}
    \infer*[left=V-Int]
    { }
    {\typeRule{\Gamma}{k}{\textsf{int}^{*}}}

    \infer*[left=V-Var]
    {\Gamma(x) = t}
    {\typeRule{\Gamma}{x}{t}}

    \infer*[left=V-Abs]
    {\typeRule{pc, \Gamma[x \mapsto t'][f \mapsto (t \to t')^l]}{e}{t}}
    {\typeRule{\Gamma}{\textsf{fix} f . \lambda x . e}{(t \to t')^l}}

    \infer*[left=V-Bracket]
    {
    \typeRule{\Gamma}{v_1}{t} \\
    \typeRule{\Gamma}{v_2}{t} \\
    l \in H \\
    l \lhd t
    }
    {\typeRule{\Gamma}{<v_1 | v_2>}{t}}

    \infer*[left=V-Sub]
    {
    \typeRule{\Gamma}{v}{t'} \\
    t' \leq t
    }
    {\typeRule{\Gamma}{v}{t}}
  \end{mathpar}
  \caption{Typing judgements for values in \langName.}
\end{figure}

The type system for our simple language is given in Figure~\ref{fig:type_rules}.

@@

We would like to thank Jon Sailor from Facebook for helping us over the phone
work through some of the more difficult problems we ran into using Coq.

\bibliographystyle{abbrv}
\bibliography{paper}
